---
title: "Alcohol vs Seat choice"
author: "Danitza Nunez"
date: "8 Sept 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


##methods

Seat is a categorical variable.
alcohol is a numerical variable.
For this problem we explain alcohol consumption based on the location people sit.
Therefore the helper file i use is numerical categorical. 

$H_0$: There is no difference between the average number of drinks based on the location of where people sit.

$H_A$: There is a difference in the average number drinks consumed by at least two rows.  



## Now with ggplot - first select the basic data


```{r}
basicCN <- ggplot(davisdata,aes(x=alcohol,y=Seat))
```



## Now add in boxplot

  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


Based on the data the individuals that sit in the back consume more alcohol than those who sit in the front or the middle. 


## Numerical Summarys 


```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

Based on the numerical summary on average the individuals in the back have about 8.5 drinks per week, the individuals in the front drink an average of 1.7 drinks a week, and the individuals in the middle drink on average 3 drinks a week. 


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Based on the ANOVA the P value is .000116 and less than .05. which means we reject the null hypothesis. 

```{r}
plot(TukeyHSD(model1))
```



## Conclusions

The evidence shows that there is a difference in alcohol consumption, individuals that drink more sit in the back.Data in the anova conclude that there is reason to reject the null hypothesis. The p-value is 0.00116 being less than the p-value of 0.05. There is no difference between the front and middle row consumption. 
